---
title: "Weight of Fish"
author: "Roxan Barakat"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

# Predicting Fish Weight
```{r}
Fish <-read.csv(file="Fish.csv",header=TRUE)
```
## Perch
```{r}
Perch <- filter(Fish, Species=="Perch")
Perch <- select(Perch,-(Species))
```

### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```

The best two regression model is height and width.

### Best Two regressor model
```{r}
best.model <- lm(Weight~Height+Width,data=Perch)
summary(best.model)
```

Out of all the models, the best 2 regression model and the best model is the same which is: Height and Width which is confirmed by the previous given graph and data.

# Five Element Perch Model
```{r}
best_Perch_Model <- lm(Weight~Height+Width,data=Perch)
Five_Element_Perch_Model <- lm(Weight~.,data=Perch)
anova(best_Perch_Model, Five_Element_Perch_Model)

```
The data shows that there's no statistical difference between the best Perch model ( 2 element model ) and the the five element Perch model; The anova test confirms this and the p-value is larger than 0.5 and closer to 1 which means there's no significant difference.  This analysis of variance shows that there's not much difference when comparing it against the 5 element model.

## Pike
```{r}
Pike <- filter(Fish, Species=="Pike")
Pike <- select(Pike,-(Species))
```

### Best Models
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topleft",main="Adjusted R^2")
```


### Best Two regressor model
```{r}
Pike_best.model <- lm(Weight~.,data=Pike)
summary(Pike_best.model)
Pike_best_2_R_model <- lm(Weight~Length1+Length3,data=Pike)
```

By comparing the best model with the best 2 element model and from the data we can infer that there's a difference between the two models. 

```{r}
Pike_best.model <- lm(Weight~.,data=Pike)
Pike_best_R_Model <- lm(Weight~Length1+Length3, data=Pike)
anova(Pike_best.model, Pike_best_2_R_model)
```

Since the p-value is less than 0.5 they're significantly different. The model with length 1,length 2, length 3, height and width is better than the model with only length 1 and length 3.

## Roach
```{r}
Roach <- filter(Fish, Species=="Roach")
Roach <- select(Roach,-(Species))
```

### Best Models
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomleft",main="Adjusted R^2")
```

Best model is 2 element model, worst model is the 5 element model, now using anova we will compare them. 

### Best Two regressor model
```{r}
roach_two_element_model <- lm(Weight~Length3+Width,data=Roach)
summary(roach_two_element_model)
```

```{r}
 roach_two_element_model<- lm(Weight~Length3+Width,data=Roach)
 roach_five_element_model<- lm(Weight~., data=Roach)
anova(roach_two_element_model, roach_five_element_model)
```
By using the anova test, we can conclude that there's no significant different between the two.

## Final Summary Statements
This exercise is about a fish salesman who's scale is broken, yet he the salesman has the ability to measure how long the fish is. My duty was to determine which is the best model to estimate and predict the weight of the fish without using a scale. We can conclude that there's no significant difference between the 2 element model