---
title: "Weight of Fish"
author: "Roxan Barakat"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

# Predicting Fish Weight
```{r}
Fish <-read.csv(file="Fish.csv",header=TRUE)
```
## Perch
```{r}
Perch <- filter(Fish, Species=="Perch")
Perch <- select(Perch,-(Species))
```

### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```

The best two regression model is height and width.

### Best Two regressor model
```{r}
best.model <- lm(Weight~Height+Width,data=Perch)
summary(best.model)
```

Out of all the models, the best 2 regression model and the best model is the same which is: Height and Width which is confirmed by the  previous given graph and data.

# Five Element Perch Model
```{r}
best_Perch_Model <- lm(Weight~Height+Width,data=Perch)
Five_Element_Perch_Model <- lm(Weight~.,data=Perch)
anova(best_Perch_Model, one_perch_model, Five_Element_Perch_Model)

```
The data shows that there's no statistical difference between the best Perch model ( 2 element model ) and the the five element Perch model; The anova test confirms this. By comparing the best perch model, one perch model, and the five element perch model tells us that the best model is the one element model.


## Pike

### Best Models

### Best Two regressor model

## Roach

### Best Models

### Best Two regressor model

## Final Summary Statements