---
title: "Weight of Fish"
author: "Roxan Barakat"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

# Predicting Fish Weight
```{r}
Fish <-read.csv(file="Fish.csv",header=TRUE)
```
## Perch
```{r}
Perch <- filter(Fish, Species=="Perch")
Perch <- select(Perch,-(Species))
```

### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```

The best two regression model is height and width.

### Best Two regressor model
```{r}
best.model <- lm(Weight~Height+Width,data=Perch)
summary(best.model)
```

Out of all the models, the best 2 regression model and the best model is the same which is: Height and Width which is confirmed by the previous given graph and data.

# Five Element Perch Model
```{r}
best_Perch_Model <- lm(Weight~Height+Width,data=Perch)
Five_Element_Perch_Model <- lm(Weight~.,data=Perch)
anova(best_Perch_Model, Five_Element_Perch_Model)

```
The data shows that there's no statistical difference between the best Perch model ( 2 element model ) and the the five element Perch model; The anova test confirms this and the p-value is larger than 0.5 and closer to 1 which means there's no significant difference.  This analysis of variance shows that there's not much difference when comparing it against the 5 element model.

## Pike
```{r}
Pike <- filter(Fish, Species=="Pike")
Pike <- select(Pike,-(Species))
```

### Best Models
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topleft",main="Adjusted R^2")
```


### Best Two regressor model
```{r}
Pike_best.model <- lm(Weight~.,data=Pike)
summary(Pike_best.model)
Pike_best_2_R_model <- lm(Weight~Length1+Length3,data=Pike)
```

## Roach

### Best Models

### Best Two regressor model

## Final Summary Statements